The relative roles of genetic, ecological and environmental factors in species radiations

### 2018-02-19 paper/draft.tex
fixes: load necessary packages etc.

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}

\title{The relative roles of genetic, ecological and environmental factors in species radiations}
\author{Ludwig Leidinger}
\date{\today}
%
\begin{document}
\maketitle

@@

%% [NEW ANGLE:]
% Island biota have always fascinated and inspired researchers (Darwin, Wallace, ...). %TODO: refs
Islands are understood as suitable model systems for ecology and evolution due to their well definable characteristics like isolation. (e.g., Losos & Ricklefs 2009) %TODO: ref
Due to global change, however, island biota are also increasingly at risk.
While often featuring unique species communities and harboring countless endemics, %TODO: refs
islands are especially threatened by climate change, human impact and invasive species. %TODO: refs
This makes understanding the functioning and evolution of island communities a high priority objective.

Recently, a group of influential island biogeography researchers proposed a set of 50 questions in island biogeography that still need answering (Patiño et al. 2017).
A subset of these questions deals with the topic of speciation and radiations on islands.
Still, the proposed mechanisms so far include only ecological or geo-morphological processes,
while genetic properties are hardly recognized in the island context.
At the same time, an increasing number of studies investigates genetic processes and
their effect on reproductive/ecological isolation of populations (e.g., Via & West 2008, Via 2001 and references therein).

@@

\subsection{scenarios}
In the simulations, we modify the value and extent of
(a) gene linkage,
(b) reproductive isolation (or reproduction compatibility),
(c) habitat diversity, and
(d) topographical complexity
to asses their relative contribution on community composition.
\Cref{tab:scenarios} summarizes the parameters which were varied for the scenarios, their meaning and their values. %TODO: make table.
Each parameter combination was replicated %TODO: how much?
times, setting a different random seed for each replicate.

@@

\begin{figure}
  \includegraphics{}
  \caption{Number of linkage units and number of species per lineage XXX timesteps after colonization.
    [Histogram (with threshold category: strongly diversified lineages) or scatter plot.]}
  \label{specieslinkage}
\end{figure}

\begin{figure}
  \includegraphics{}
  \caption{Trait space characteristics of lineages.
    (A) [Ordination] Trait space of successful colonizers compared to the mainland species pool. Each point represents a lineage.
    Arrows denote the traits.
    (B) [Ordination?] Linkage of traits of successful colonizers(/radiators?). Traits perpendicular to each other are inherited independently,
  same direction indicate tight linkage of traits.}
  \label{traitspace}
\end{figure}

>>>>

\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage{cleveref}

\title{The relative roles of genetic, ecological and environmental factors in species radiations}
\author{Ludwig Leidinger}
\date{\today}
%

\begin{document}
\maketitle

@@

%% [NEW ANGLE:]
% Island biota have always fascinated and inspired researchers (Darwin, Wallace, ...). %TODO: refs
Islands are understood as suitable model systems for ecology and evolution due to their well definable characteristics like isolation. (e.g., Losos \& Ricklefs 2009) %TODO: ref
Due to global change, however, island biota are also increasingly at risk.
While often featuring unique species communities and harboring countless endemics, %TODO: refs
islands are especially threatened by climate change, human impact and invasive species. %TODO: refs
This makes understanding the functioning and evolution of island communities a high priority objective.

Recently, a group of influential island biogeography researchers proposed a set of 50 questions in island biogeography that still need answering (Patiño et al. 2017).
A subset of these questions deals with the topic of speciation and radiations on islands.
Still, the proposed mechanisms so far include only ecological or geo-morphological processes,
while genetic properties are hardly recognized in the island context.
At the same time, an increasing number of studies investigates genetic processes and
their effect on reproductive/ecological isolation of populations (e.g., Via \& West 2008, Via 2001 and references therein).

@@

\subsection{scenarios}
In the simulations, we modify the value and extent of
(a) gene linkage,
(b) reproductive isolation (or reproduction compatibility),
(c) habitat diversity, and
(d) topographical complexity
to asses their relative contribution on community composition.
\cref{tab:scenarios} summarizes the parameters which were varied for the scenarios, their meaning and their values. %TODO: make table.
Each parameter combination was replicated %TODO: how much?
times, setting a different random seed for each replicate.

@@

\begin{figure}
  %\includegraphics{}
  \caption{Number of linkage units and number of species per lineage XXX timesteps after colonization.
    [Histogram (with threshold category: strongly diversified lineages) or scatter plot.]}
  \label{specieslinkage}
\end{figure}

\begin{figure}
  %\includegraphics{}
  \caption{Trait space characteristics of lineages.
    (A) [Ordination] Trait space of successful colonizers compared to the mainland species pool. Each point represents a lineage.
    Arrows denote the traits.
    (B) [Ordination?] Linkage of traits of successful colonizers(/radiators?). Traits perpendicular to each other are inherited independently,
  same direction indicate tight linkage of traits.}
  \label{traitspace}
\end{figure}
